PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization

### 2024-09-03 tex/poster.tex
Add missing R back in

        \textbf{The lemma is optimal:}
        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
          Add a node $x \in B$ connected to $L, M, R$. With the correct numbers of vertices in
          $L, M, $ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
        $v$ has to go before $u$.

>>>>

        \textbf{The lemma is optimal:}
        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
          Add a node $x \in B$ connected to $L, M, R$. With the correct numbers of vertices in
          $L, M, R$ we can make it so that $c(v, x, u) < \min(c(x, u, v), c(u, v, x))$, so that
        $v$ has to go before $u$.
